 

### 2023-07-17 markdown/discussion.Rmd
app on desktop pc established

# read in MS result table
mqScpData <- read.delim("/home/lukas/Desktop/MS-Data/Lukas/Jun13/combined/txt/evidence.txt")

sampleAnnotation = read.delim("/home/lukas/Desktop/MS-Data/Lukas/Jun13/combined/txt/sampleAnnotation.txt")

>>>>

folder <- "/media/lukas/DAB0041DB003FEAF/MS-Data"

# read in MS result table
mqScpData <- read.delim("/media/lukas/DAB0041DB003FEAF/MS-Data/Lukas/Jun13/combined/txt/evidence.txt")

sampleAnnotation = read.delim("/media/lukas/DAB0041DB003FEAF/MS-Data/Lukas/Jun13/combined/txt/sampleAnnotation.txt")
